### 2019-06-08 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Done for ch5

\begin{lemma}\label{lem:5:SubOptimalSelections}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
  For any $\boldsymbol{\mu}\in\cP_M$,
  let player $j\in[M]$ use the \RandTopM-, \MCTopM- or \rhoRand-\klUCB{}
  decentralized policy with exploration function $f(t) = \log(t) + 3 \log\log(t)$.
  Then for any sub-optimal arm $k \in \Mworst$, there exists two problem-dependent positive constants $C_{\boldsymbol{\mu}}, D_{\boldsymbol{\mu}} > 0$ such that
  % %
  % \hfill{}
  % (Proved in Appendix~\ref{proof:5:SubOptimalSelections})
  \begin{equation}\label{eq:5:SubOptimalSelections}
      \E_{\mu}[T_k^j(T)] \leq
      \frac{\log(T)}{\kl(\mu_k,\mu_{M}^*)}
      + \underbrace{C_{\boldsymbol{\mu}} \sqrt{\log(T)} + D_{\boldsymbol{\mu}}\log\log(T) + 3M + 1}_{= \smallO{\log(T)}}.
  \end{equation}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

  Considering the relative position of the upper-confidence bound $U_{m^*}^j(t)$ and the corresponding mean $\mu_m^* = \mu_{m^*}$, one can write the decomposition

  \begin{align}
    \E_{\mu}[T_k^j(T)] &\leq
    \sum_{t=1}^T\Pr_{\bm{\mu}} \left( \exists m_1 \in [M]: \; U_{m_1^*}(t) < \mu_m^* \right) + \notag \\
    \;\;\;\;
    \sum_{t=1}^T\Pr_{\bm{\mu}} & \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; U_{m_2^*}(t) \leq U_k(t) , \forall {m_3} \in [M]: \;  U_{{m_3}^*}(t) \geq \mu_{m_3}^* \right) \notag \\
    &\leq \sum_{m_1=1}^M\sum_{t=1}^T\Pr_{\bm{\mu}} \left(U_{m_1^*}(t) < \mu_{m_1}^* \right) + \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; \mu_{m_2}^* \leq U_k(t)\right) \notag \\
    %
    & \leq \sum_{m_1=1}^M \sum_{t=1}^T \Pr_{\bm{\mu}} \left( U_{m_1^*}(t) < \mu_{m_1}^* \right)
    + \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\; \mu_{M^*} \leq U_k(t) \right)
    \label{eq:5:sumOfProbaForTkj}
  \end{align}
  where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in [M]$.

@@

  \begin{lemma}\label{lem:5:Fact1KLUCB}
  \begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
      For any arm $k$, if $U_k^{j}(t)$ is the \klUCB{} index with exploration function $f(t)=\log(t)+3\log\log(t)$,
      \begin{equation}
        \sum_{t=1}^T \Pr_{\bm{\mu}} \left(U_k^{j}(t) < \mu_k\right) \leq 3 + 4e \log\log(T).
      \end{equation}
  \end{leftbar}  % XXX leftbar lemmabar, comment if needed
  \end{lemma}

@@

  Putting things together, one obtains the non-asymptotic upper bound
  \begin{align}\label{eq:5:UBprecise}
    \E_{\mu}\left[T_k^j(T)\right]
    & \leq \frac{\log(T) + 3 \log\log(T)}{\kl(\mu_k,\mu_{M^*})} + \sqrt{2\pi} \sqrt{\frac{\kl'(\mu_k,\mu_{M^*})^2}{\kl(\mu_k,\mu_{M*})^3}}\sqrt{\log(T) + 3\log\log(T)}  \nonumber\\
    & \;\;\;\;\;\;+ 2\left(\frac{\kl'(\mu_k,\mu_{M^*})}{\kl(\mu_k,\mu_{M^*})}\right)^2 + 4Me \log\log(T) + 3M+1,
  \end{align}
  which yields Lemma~\ref{lem:5:SubOptimalSelections},
  with explicit constants $C_{\boldsymbol{\mu}}$ and $D_{\boldsymbol{\mu}}$.
\end{smallproof}

@@

\begin{smallproof}
  We analyze the case when the current arm leaves the set $\TopM$ (Line 4):

  \begin{align*}
    & \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t)\right)  \\ & \leq \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t), A^j(t+1) \in \TopM(t) \cap \{k': U_{k'}^j(t-1) \leq U_k^j(t-1)\}\right) \\
    & \leq   \sum_{t=1}^T \sum_{k' \neq k}\Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right) \\
    & = \sum_{k' \neq k} \underbrace{\sum_{t=1}^T \Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right)}_{:= T_{k'}}
  \end{align*}

  Now, to control $T_{k'}$, we distinguish two cases. If $\mu_k < \mu_{k'}$, one can write
  \[T_{k'} \leq \sum_{t=1}^T \Pr\left(U_{k'}^j(t) \leq \mu_{k'}\right) + \sum_{t=1}^T \Pr\left(A^j(t) = k, U_{k}^j(t-1) \geq \mu_{k'}\right)\]
  The first term in the right hand side is $o(\log(T))$ by Lemma~\ref{lem:5:Fact1KLUCB}. To control the second term, we apply the same trick that led to the proof of Lemma~\ref{lem:5:Fact2KLUCB} in \cite{KLUCBJournal}.
  Letting $\kl^+(x, y) := \kl(x, y) \indic(x \geq y)$,
  and $\widehat{\mu}^j_{k,s}$ be the empirical mean of the $s$ first observations from arm $k$ by player $j$, one has

  \begin{align}
    \sum_{t=1}^T & \Pr\left(A^j(t) = k, U_{k}^j(t-1) \geq \mu_{k'}\right) \nonumber\\
    & =  \bE \left[ \sum_{t=1}^T\sum_{s=1}^{t-1} \indic{\left(A^j(t) = k , N^j_k(t-1) = s\right)}\indic{\left( s  \times \kl^+\left(\widehat{\mu}_{k,s}^j , \mu_k\right) \leq f(t)\right)} \right]\nonumber\\
    & \leq \bE \left[ \sum_{s=1}^{T}\indic{\left( s \times \kl^+\left(\widehat{\mu}_{k,s}^j , \mu_k\right) \leq f(T)\right)}\sum_{t=s-1}^T \indic{\left(A^j(t) = k , N^j_k(t-1) = s\right)} \right] \nonumber \\
    & \leq \sum_{s=1}^T \Pr\left( s \times \kl^+\left(\widehat{\mu}_{k,s}^j , \mu_k\right) \leq f(T)\right),\label{eq:5:FromHere}
  \end{align}
  where the last inequality uses that for all $s$, \[\sum_{t=s-1}^T \indic{\left(A^j(t) = k , N^j_k(t-1) = s\right)} = \sum_{t=s-1}^T \indic{\left(A^j(t) = k , N^j_k(t) = s + 1\right)} \leq 1.\]
  From \eqref{eq:5:FromHere}, the same upper bound as that of Lemma~\ref{lem:5:Fact2KLUCB} can be obtained using the tools from \cite{KLUCBJournal}, which proves that for $T\to\infty$,
  \[T_{k'} = \frac{\log(T)}{\kl(\mu_k,\mu_{k'})} + o(\log(T)).\]

  If $\mu_k > \mu_{k'}$, we rather use that
  \[T_{k'} \leq \sum_{t=1}^T \Pr\left(U_{k}^j(t) \leq \mu_{k}\right) + \sum_{t=1}^T \Pr\left(A^j(t+1) = k', U_{k'}^j(t) \geq \mu_{k}\right)\]
  and similarly Lemma~\ref{lem:5:Fact1KLUCB} and a slight variant of Lemma~\ref{lem:5:Fact2KLUCB} to deal with the modified time indices yields
  \[T_{k'} = \frac{\log(T)}{\kl(\mu_{k'},\mu_{k})} + o(\log(T)).\]
  Summing over $k'$ yields the result.
\end{smallproof}

@@

  For player $j$ and round $t$, we now introduce a few events that are useful in the proof. First, for every $x=1,2,3,4,5$, we denote $I_x^j(t)$ the event that a transition of type $(x)$ occurs for player $j$ after the first $t$ observations (\ie, between round $t$ and round $t+1$, to decide $A^j(t+1)$).
  Formally they are defined by
  \begin{align*}
    I_1^j(t) &:= \left(\overline{s^j(t)},\overline{C_j(t)}, A^j(t) \in \TopM(t)\right), \\
    % go sitted
    I_2^j(t) &:= \left(\overline{s^j(t)},C_j(t), A^j(t) \in \TopM(t)\right),
    \ \ \ &\text{and} \ \ \
    I_3(t) &:= \left(\overline{s^j(t)},A^j(t) \notin \TopM(t)\right), \\
    % if sitted
    I_3(t) &:= \left(s^j(t),A^j(t) \in \TopM(t)\right),
    \ \ \ &\text{and} \ \ \
    I_5(t) &:= \left(s^j(t),A^j(t) \notin \TopM(t)\right).
  \end{align*}
  %
  Then, we introduce $\widetilde{C^j}(t)$ as the event that a collision occurs for player $j$ at round $t$ if she is not yet fixed on her arm, that is
  \begin{equation}
      \widetilde{C^j}(t) := \left(C^j(t), \overline{s^j(t)}\right).
  \end{equation}

@@

  Now we can decompose the sum on $t=1,\dots,T$ with the use of consecutive sequences,
  \[
    \E_{\mu}[N_2^j(t)]
    = \E_{\mu}\left[ \sum_{t=1}^T \indic{\left(I_2^j(t)\right)} \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} \left( \sum_{t=\theta_i}^{\tau_i - 1} 1 + \sum_{t=\tau_i}^{\theta_{i+1} - 1} 0 \right) \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} (\tau_i - \theta_i) \right].
  \]
  Both $n(T)$ and $\tau_i - \theta_i \geq 0$ have finite averages for any $i$ (as $\tau_i - \theta_i \leq T$), and $n(T)$ is a \emph{stopping time} with respect to the past events (that is, $\cF^j_T$),
  thus we can use Wald's Lemma \citep{Wald45},
  to obtain a decomposition with two terms $(\alpha)$ and $(\beta)$:
  \[
    \E_{\mu}[N_2^j(t)] \leq \underbrace{\E_{\mu}\left[ n(T) \right]}_{(\alpha)} \times \underbrace{\max_{i\in\N} \E_{\mu}\left[ \tau_i - \theta_i \right]}_{(\beta)}.
  \]

@@

\paragraph{Logarithmic switching cost for \MCTopM.}\label{app:5:NumberSwitches}
%
Additionally to bounding the collisions in Lemma~\ref{lem:5:collisionsMCTopM},
another consequence of our proof of this result is that
it also bounds the (expected) number of \emph{switches of arms}, $SC^{\cA}(T) = \sum_{t=1}^T \Pr(A^j(t+1) \neq A^j(t))$.
%
We controlled the total number of transitions $(2)$, $(3)$ and $(5)$,
which are the only transitions when a player can switch from arm $k$ to arm $k'\neq k$.
Thus, the total number of arm switches is also proven to be logarithmic, if all players uses the \MCTopM-\klUCB{} algorithm.
This additional guarantee was never clearly stated for previous state-of-the-art works, like \rhoRand.
%
Even though minimizing the number of arms switching was not a goal,
this guarantee is appealing, in particular for Cognitive Radio applications,
where switching arms means re-configuring a radio hardware, an operation that costs energy.
An algorithm guaranteeing a small number of switches is thus interesting,
and for instance \cite{modiDemo2016} studied the empirical impact of the number of hardware reconfigurations on the battery life of a dynamic end-devices.
This work highlighted a tradeoff between minimizing regret and minimizing the number of switches of arms.
%
We also note that introducing explicit \emph{switching costs} in the regret, like it was done in previous works like \cite{Koren17} for single-player bandits, could also be fruitful.

@@

\paragraph{Other experiments.}
%
We now present more results for two bandit instances.
\begin{itemize}
  \item
  The first instance is a small problem one with $K=3$ arms and means
  $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$, for the case of $M=2$ players.
  It is used to illustrate that in some unlucky runs, \Selfish{} can suffer a linear regret, as illustrated in Figure~\ref{fig:5:selfish_fail1}.
  \item
  The second instance considers $K=9$ arms with means $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$,
  three cases are presented: $M=6$ in Figure~\ref{fig:5:MP__K9_M6_T10000_N1000__4_algos},
  and for the two limit cases $M=2$ and $M=9=K$ in Figure~\ref{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}.
\end{itemize}
%
We also include histograms showing the \emph{distribution} of the final regret $R_T$,
as this allows to check if the regret is indeed small for \emph{each} run of the simulation.
%
For the plots showing the regret, our \emph{asymptotic} lower bound from Theorem~\ref{thm:5:BetterLowerBound} is displayed.

@@

\paragraph{Uniformly sampled problems.}
%
Experiments with a different problem for each repetition,
that is uniformly sampled $\boldsymbol{\mu} \sim \cU([0,1]^K)$,
are also considered, in Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} and \ref{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}.
This helps to check that no matter the \emph{complexity} of the considered problem (one measure of complexity being the constant in our lower bound),
\MCTopM{} performs similarly or better than all the other algorithms,
and \Selfish{} outperforms \rhoRand{} in most cases.
Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} is a good example
of outstanding performances of \MCTopM{} and \Selfish{} in comparison to \rhoRand{}.
%
Empirically, our proposals were found to always outperform \rhoRand{}, and except for \Selfish{} that can fail badly on problems with small $K$,
we verified that \MCTopM{} outperforms the state-of-the-art algorithms in many different problems, and is more and more efficient as $M$ and $K$ grows.

>>>>

\begin{lemma}\label{lem:5:SubOptimalSelections}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
  For any $\boldsymbol{\mu}\in\cP_M$,
  let player $j\in[M]$ use the \RandTopM-, \MCTopM- or \rhoRand-\klUCB{}
  decentralized policy with exploration function $f(t) = \log(t) + 3 \log(\log(t))$.
  Then for any sub-optimal arm $k \in \Mworst$ there exists problem-dependent constants $C_{\boldsymbol{\mu}}, D_{\boldsymbol{\mu}} > 0$ such that
  % %
  % \hfill{}
  % (Proved in Appendix~\ref{proof:5:SubOptimalSelections})
  \begin{equation}\label{eq:5:SubOptimalSelections}
      \E_{\mu}[T_k^j(T)] \leq
      \frac{\log(T)}{\kl(\mu_k,\mu_{M}^*)}
      + \underbrace{C_{\boldsymbol{\mu}} \sqrt{\log(T)} + D_{\boldsymbol{\mu}}\log(\log(T)) + 3M + 1}_{= \smallO{\log(T)}}.
  \end{equation}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

  Considering the relative position of the upper-confidence bound $U_{m^*}^j(t)$ and the corresponding mean $\mu_m^* = \mu_{m^*}$, one can write the decomposition
  \begin{align*}
    \E_{\mu}[T_k^j(T)] &\leq
    \sum_{t=1}^T\Pr_{\bm{\mu}} \left( \exists m_1 \in [M]: \; U_{m_1^*}(t) < \mu_m^* \right) + \\
    \;\;\;\;
    \sum_{t=1}^T\Pr_{\bm{\mu}} & \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; U_{m_2^*}(t) \leq U_k(t) , \forall {m_3} \in [M]: \;  U_{{m_3}^*}(t) \geq \mu_{m_3}^* \right)
  \end{align*}
  \begin{align}
    \E_{\mu}[T_k^j(T)] &\leq \sum_{m_1=1}^M\sum_{t=1}^T\Pr_{\bm{\mu}} \left(U_{m_1^*}(t) < \mu_{m_1}^* \right) + \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; \mu_{m_2}^* \leq U_k(t)\right) \notag \\
    %
    & \leq \sum_{m_1=1}^M \sum_{t=1}^T \Pr_{\bm{\mu}} \left( U_{m_1^*}(t) < \mu_{m_1}^* \right)
    + \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\; \mu_{M^*} \leq U_k(t) \right)
    \label{eq:5:sumOfProbaForTkj}
  \end{align}
  where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in [M]$.

@@

  \begin{lemma}\label{lem:5:Fact1KLUCB}
  \begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
      For any arm $k$, if $U_k^{j}(t)$ is the \klUCB{} index with exploration function $f(t)=\log(t)+3\log(\log(t))$,
      \begin{equation}
        \sum_{t=1}^T \Pr_{\bm{\mu}} \left(U_k^{j}(t) < \mu_k\right) \leq 3 + 4e \log(\log(T)).
      \end{equation}
  \end{leftbar}  % XXX leftbar lemmabar, comment if needed
  \end{lemma}

@@

  Putting things together, one obtains the non-asymptotic upper bound
  \begin{align}\label{eq:5:UBprecise}
    \E_{\mu}\left[T_k^j(T)\right]
    & \leq \frac{\log(T) + 3 \log(\log(T))}{\kl(\mu_k,\mu_{M^*})} + \sqrt{2\pi} \sqrt{\frac{\kl'(\mu_k,\mu_{M^*})^2}{\kl(\mu_k,\mu_{M*})^3}}\sqrt{\log(T) + 3\log(\log(T))}  \nonumber\\
    & \;\;\;\;\;\;+ 2\left(\frac{\kl'(\mu_k,\mu_{M^*})}{\kl(\mu_k,\mu_{M^*})}\right)^2 + 4Me \log(\log(T)) + 3M+1,
  \end{align}
  which yields Lemma~\ref{lem:5:SubOptimalSelections},
  with explicit constants $C_{\boldsymbol{\mu}}$ and $D_{\boldsymbol{\mu}}$.
\end{smallproof}

@@

\begin{smallproof}
  We analyze the case when the current arm leaves the set $\TopM$ (Line 4):
  %
  \begin{align*}
    & \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t)\right)  \\ & \leq \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t), A^j(t+1) \in \TopM(t) \cap \{k': U_{k'}^j(t-1) \leq U_k^j(t-1)\}\right) \\
    & \leq   \sum_{t=1}^T \sum_{k' \neq k}\Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right) \\
    & = \sum_{k' \neq k} \underbrace{\sum_{t=1}^T \Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right)}_{:= T_{k'}}
  \end{align*}

  Now, to control $T_{k'}$, we distinguish two cases. If $\mu_k < \mu_{k'}$, one can write
  \[T_{k'} \leq \sum_{t=1}^T \Pr\left(U_{k'}^j(t) \leq \mu_{k'}\right) + \sum_{t=1}^T \Pr\left(A^j(t) = k, U_{k}^j(t-1) \geq \mu_{k'}\right)\]
  The first sum is $o(\log(T))$ by Lemma~\ref{lem:5:Fact1KLUCB}.
  To control the second sum, we apply the same trick that led to the proof of Lemma~\ref{lem:5:Fact2KLUCB} in \cite{KLUCBJournal}.
  Letting $\kl^+(x, y) := \kl(x, y) \indic(x \geq y)$,
  and $\widehat{\mu}^j_{k,s}$ be the empirical mean of the $s$ first observations from arm $k$ by player $j$, one has
  %
  \begin{align*}
    \sum_{t=1}^T & \Pr\left(A^j(t) = k, U_{k}^j(t-1) \geq \mu_{k'}\right) \\
    & =  \bE \left[ \sum_{t=1}^T\sum_{s=1}^{t-1} \indic{\left(A^j(t) = k , N^j_k(t-1) = s\right)}\indic{\left( s  \times \kl^+\left(\widehat{\mu}_{k,s}^j , \mu_k\right) \leq f(t)\right)} \right]
  \end{align*}
  \begin{align}
    & \leq \bE \left[ \sum_{s=1}^{T}\indic{\left( s \times \kl^+\left(\widehat{\mu}_{k,s}^j , \mu_k\right) \leq f(T)\right)}\sum_{t=s-1}^T \indic{\left(A^j(t) = k , N^j_k(t-1) = s\right)} \right] \nonumber \\
    & \leq \sum_{s=1}^T \Pr\left( s \times \kl^+\left(\widehat{\mu}_{k,s}^j , \mu_k\right) \leq f(T)\right),\label{eq:5:FromHere}
  \end{align}
  where the last inequality uses that for all $s$, \[\sum_{t=s-1}^T \indic{\left(A^j(t) = k , N^j_k(t-1) = s\right)} = \sum_{t=s-1}^T \indic{\left(A^j(t) = k , N^j_k(t) = s + 1\right)} \leq 1.\]
  From \eqref{eq:5:FromHere}, the same upper bound as that of Lemma~\ref{lem:5:Fact2KLUCB} can be obtained using the tools from \cite{KLUCBJournal}, which proves that for $T\to\infty$,
  \[T_{k'} = \frac{\log(T)}{\kl(\mu_k,\mu_{k'})} + o(\log(T)).\]

  If $\mu_k > \mu_{k'}$, we rather use that
  $T_{k'} \leq \sum\limits_{t=1}^T \Pr\left(U_{k}^j(t) \leq \mu_{k}\right) + \sum\limits_{t=1}^T \Pr\left(A^j(t+1) = k', U_{k'}^j(t) \geq \mu_{k}\right)$,
  and similarly Lemma~\ref{lem:5:Fact1KLUCB} and a slight variant of Lemma~\ref{lem:5:Fact2KLUCB} to deal with the modified time indices yields
  $T_{k'} = \frac{\log(T)}{\kl(\mu_{k'},\mu_{k})} + o(\log(T))$.
  Summing over $k'$ yields the result.
\end{smallproof}

@@

  For player $j$ and round $t$, we now introduce a few events that are useful in the proof. First, for every $x=1,2,3,4,5$, we denote $I_x^j(t)$ the event that a transition of type $(x)$ occurs for player $j$ after the first $t$ observations (\ie, between round $t$ and round $t+1$, to decide $A^j(t+1)$).
  Formally they are defined by
  \begin{align*}
    I_1^j(t) &:= \left(\overline{s^j(t)},\overline{C_j(t)}, A^j(t) \in \TopM(t)\right), \\
    % go sitted
    I_2^j(t) &:= \left(\overline{s^j(t)},C_j(t), A^j(t) \in \TopM(t)\right),
    \ \ \ &\text{and} \ \ \
    I_3(t) &:= \left(\overline{s^j(t)},A^j(t) \notin \TopM(t)\right), \\
    % if sitted
    I_3(t) &:= \left(s^j(t),A^j(t) \in \TopM(t)\right),
    \ \ \ &\text{and} \ \ \
    I_5(t) &:= \left(s^j(t),A^j(t) \notin \TopM(t)\right).
  \end{align*}
  %
  Then, we introduce $\widetilde{C^j}(t)$ as the event that a collision occurs for player $j$ at round $t$ if she is not yet fixed on her arm, that is
  % \begin{equation}
  $\widetilde{C^j}(t) := \left(C^j(t), \overline{s^j(t)}\right)$.
  % \end{equation}

@@

  Now we can decompose the sum on $t=1,\dots,T$ with the use of consecutive sequences,
  \[
    \E_{\mu}[N_2^j(t)]
    = \E_{\mu}\left[ \sum_{t=1}^T \indic{\left(I_2^j(t)\right)} \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} \left( \sum_{t=\theta_i}^{\tau_i - 1} 1 + \sum_{t=\tau_i}^{\theta_{i+1} - 1} 0 \right) \right]
    =
    \E_{\mu}\left[ \sum_{i=1}^{n(T)} (\tau_i - \theta_i) \right].
  \]
  Both $n(T)$ and $\tau_i - \theta_i \geq 0$ have finite averages for any $i$ (as $\tau_i - \theta_i \leq T$), and $n(T)$ is a \emph{stopping time} with respect to the past events (that is, $\cF^j_T$),
  thus we can use Wald's Lemma \citep{Wald45},
  to obtain a decomposition with two terms $(\alpha)$ and $(\beta)$,
  $\E_{\mu}[N_2^j(t)] \leq \E_{\mu}\left[ n(T) \right] \times \max_{i\in\N} \E_{\mu}\left[ \tau_i - \theta_i \right]$.
  % $\E_{\mu}[N_2^j(t)] \leq \underbrace{\E_{\mu}\left[ n(T) \right]}_{(\alpha)} \times \underbrace{\max_{i\in\N} \E_{\mu}\left[ \tau_i - \theta_i \right]}_{(\beta)}$.

@@

\paragraph{Logarithmic switching cost for \MCTopM.}\label{app:5:NumberSwitches}
%
While Lemma~\ref{lem:5:collisionsMCTopM} bounds the number of collisions,
another consequence of our proof is that we have also bounded
the (expected) number of \emph{switches of arms}, $SC^{\cA}(T) = \sum_{t=1}^T \Pr(A^j(t+1) \neq A^j(t))$.
%
We controlled the total number of transitions $(2)$, $(3)$ and $(5)$,
which are the only transitions when a player can switch from arm $k$ to arm $k'\neq k$.
Thus, the total number of arm switches is also proven to be logarithmic, if all players uses the \MCTopM-\klUCB{} algorithm.
This additional guarantee was never clearly stated for previous state-of-the-art works, like \rhoRand.
%
Even though minimizing the number of arms switching was not a goal,
this guarantee is appealing, in particular for Cognitive Radio applications,
where switching arms means re-configuring a radio hardware, an operation that costs energy.
An algorithm guaranteeing a small number of switches is thus interesting,
and for instance \cite{modiDemo2016} studied the empirical impact of the number of hardware reconfigurations on the battery life of a dynamic end-devices.
This work highlighted a tradeoff between minimizing regret and minimizing the number of switches of arms.
%
We also note that introducing explicit \emph{switching costs} in the regret, like it was done in previous works like \cite{Koren17} for single-player bandits, could also be fruitful.

@@

\textbf{Other experiments.}
%
We now present more results for two bandit instances.
% \begin{itemize}
%   \item
  The first instance is a small problem one with $K=3$ arms and means
  $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$, for the case of $M=2$ players.
  It is used to illustrate that in some unlucky runs, \Selfish{} can suffer a linear regret, as illustrated in Figure~\ref{fig:5:selfish_fail1}.
  % \item
  The second instance considers $K=9$ arms with means $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$,
  three cases are presented: $M=6$ in Figure~\ref{fig:5:MP__K9_M6_T10000_N1000__4_algos},
  and for the two limit cases $M=2$ and $M=9=K$ in Figure~\ref{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}.
% \end{itemize}
%
We also include histograms showing the \emph{distribution} of the final regret $R_T$,
as this allows to check if the regret is indeed small for \emph{each} run of the simulation.
%
For the plots showing the regret, our \emph{asymptotic} lower bound from Theorem~\ref{thm:5:BetterLowerBound} is displayed.

@@

\textbf{Uniformly sampled problems.}
%
Experiments with a different problem for each repetition,
that is uniformly sampled $\boldsymbol{\mu} \sim \cU([0,1]^K)$,
are also considered, in Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} and \ref{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}.
This helps to check that no matter the \emph{complexity} of the considered problem (one measure of complexity being the constant in our lower bound),
\MCTopM{} performs similarly or better than all the other algorithms,
and \Selfish{} outperforms \rhoRand{} in most cases.
Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} is a good example
of outstanding performances of \MCTopM{} and \Selfish{} in comparison to \rhoRand{}.
%
Empirically, our proposals were found to always outperform \rhoRand{}, and except for \Selfish{} that can fail badly on problems with small $K$,
we verified that \MCTopM{} outperforms the state-of-the-art algorithms in many different problems, and is more and more efficient as $M$ and $K$ grows.

### 2019-06-08 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Done for ch5

%
% System regret and three terms
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_2092905764868974160.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_1699475021767911583.pdf}
    % \end{subfigure}
    \caption[Multi-player regret with its three terms]{Regret with its three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3}, and lower bounds \eqref{eq:5:ourLowerBound} and \eqref{eq:5:Zhao10LowerBound} in \textbf{black}, for \Selfish-\klUCB: $M=6$ and $M=9$ players, $K=9$ arms, horizon $T=10000$ (for $1000$ runs).}
    \label{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

>>>>

%
% System regret and three terms
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_2092905764868974160.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_1699475021767911583.pdf}
    % \end{subfigure}
    \caption[Illustrating the decomposition of the multi-player regret with its three terms]{The three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} of the multi-player regret, and lower bounds \eqref{eq:5:ourLowerBound} and \eqref{eq:5:Zhao10LowerBound} in \textbf{black}, for \Selfish-\klUCB: $M=6$ and $M=9$ players, $K=9$ arms, horizon $T=10000$ (for $1000$ runs).}
    \label{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}
